Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) calculated on unit level, which we call the delta maintainability score. Based on this score, we extract common factors between clones and the derived thresholds for them, based on which a developer could filter their clone output.

% Experimental setup: how we validated that we fixed the problem
To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. Because not all clones can easily be automatically refactored, we define those that can. Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and computes the delta maintainability scores.

>>>>

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) calculated on unit level, which we call the delta maintainability score. Based on this score, we extract common factors between clones and derive thresholds for them, based on which a developer could filter their clone output.

% Experimental setup: how we validated that we fixed the problem
To analyse such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. Because not all clones can easily be automatically refactored, we define those that can. Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and computes the delta maintainability scores.
